---
title: "Title (E. Kreiss, J. Degen, M. Franke)"
output: html_notebook
---
## 1. Introduction

If you have any questions or comments related to this work, please consult [Elisa Kreiss](http://www.elisakreiss.com/index.html).

#### 1.1 Abstract

#### 1.2 Further information

For a manuscript, please contact [Elisa Kreiss](http://www.elisakreiss.com).

## 2. Import, clean and categorize empirical data

#### 2.1 Basic setup 
* import libraries & data, exclude data that cannot be used for analysis

```{r}
library(dplyr)
library(ggplot2)
library(bootstrap)
library(lme4)
library(tidyr)
library(here)

theme_set(theme_bw(18))
source(here("Rscripts","helpers.r"))

# d = read.table(file=here("Data","results.csv"),sep="\t", header=T, quote="")

```

## 3 Plots

#### 3.1 Plot something

## 4 BDA 
#### 4.1 BDA data preparation

## 4.2 Statistical analysis

```{r}
# m = glmer(ColorOrType ~ cNormedTypicality + cInformative + cCC + (1|gameid) + (1|Item), data = centered, family="binomial")
# summary(m)
# ranef(m)

# anova(m,m.1)
```